\documentclass[stu,12pt,floatsintext]{apa7}

\usepackage[american]{babel}
\usepackage{csquotes}
\usepackage[style=apa,sortcites=true,sorting=nyt,backend=biber]{biblatex}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{cite}
\usepackage[T1]{fontenc} 
\usepackage{mathptmx} 

\title{Artificial Intelligence-Driven Detection of Genetic Mutations in Glioblastoma Multiforme Using Genomic Data}
\shorttitle{AI Detection of Mutations in GBM}
\author{Pranav Gundu}
\date{October 10, 2024}
\affiliation{Shrewsbury Public High School}
\course{Research Methods \& Biology Honors 3058}
\professor{Ms. Lambert-Peloquin}

\abstract{This paper explores the application of AI in detecting genetic mutations in Glioblastoma Multiforme (GBM) using genomic data. The abstract summarizes the introduction, methods, results, and discussion.}

\begin{document}
\maketitle

\section{Introduction}
This paper introduces the use of artificial intelligence in medical genetics, focusing on the detection of mutations in glioblastoma multiforme. References to prior studies will be made throughout the paper \parencite{Sample2024}, \parencite{FullBook2021}.

\section{Method}
\subsection{Participants}
This section describes the study's participants, including demographics and recruitment details.

\subsection{Materials}
Details of materials used, such as the genomic data sources and the AI model, are provided here.

\subsection{Procedure}
This section outlines the procedural steps followed, including data collection and model training.

\section{Results}
\subsection{Descriptive Statistics}
A table of the key descriptive statistics for the data used is included.

\begin{table}
    \caption{Descriptive statistics for genetic mutation detection.}
    \centering
    \begin{tabular}{cc}
        \hline 
        Mutation Type & Frequency \\
        \hline
        TP53 & 45\% \\
        IDH1 & 30\% \\
        \hline
    \end{tabular}
\end{table}

\subsection{Inferential Statistics}
Statistical tests show significant differences in mutation detection between methods, \ttestSig{111}{3.21}.

\section{Discussion}
This section discusses the implications of the findings and ties them into existing research, with suggestions for future work.

\printbibliography
\end{document}
